% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[11pt]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\usepackage{latexsym}
\begin{document}

\name{Gregory A. Haynes}
\address{2030 NW Flanders St. \#103 \\  Portland, OR. 97209 \\  (503) 928-4240 \\  greg@greghaynes.net \\ http://greghaynes.net }

\begin{resume}

\section{OBJECTIVE} Employment as a software developer with an emphasis on software engineering.

\section{EDUCATION} \begin{itemize}
                        \item Will graduate with Bachelor of Science degrees in Computer Science and Physics from Portland State University in June, 2012.
                    \end{itemize}

\section{SKILLS} {\bf Programming:} \textit{C, C++, Java, Python, PHP.} \\
                   Developed C++ applications using Qt and KDE.  Created graphical client, and server applications in Java using Swing and Google AppEngine.  Studied physics simulation devolpment in Python, and developed server applications using Django.  Developed custom CMSes using PHP. \\
                 \\
                 {\bf Systems Administration:} \textit{Linux, FreeBSD.} \\
                   Maintained DNS, Web, SQL Databases, and Email systems. DNS mantained using BIND9.  Web server experince using Apache and Lighttpd with PHP and Python support.  SQL databases using MySQL and PostgreSQL.  Email systems using QMail, Postfix and Sendmail. \\
                 \\
                 {\bf Web Development:} \textit{HTML/XML, JavaScript, CSS, GWT} \\
                 Web applications using GWT, JavaScript, HTML, and CSS built ontop of Java,  Python, or PHP server applications. \\
                 \\
                 {\bf Open Source Development} \\
                 Development in large open source projects (KDE) and lead developer of small open source projects (Kobby).

\section{EXPERIENCE} {\bf 2007 to Date Greenpros Landscaping,} Bellaire, TX. \\
                     Systems administrator, maintained and built computer systems for use by management.  Developed product and directly interacted with customer using it. \\
                     \\
                     {\bf Summer 2008 Google Summer Of Code.} \\
                     Developed collaborative text editing framework for KDE E.V.  Designed project from start and coordinated development with KTextEditor team for changes in the KDE API.  Project remains under active development.
\end{resume} 
\end{document}









