\documentclass[a4paper,10pt]{article}


%opening
\title{Research Paper Proposal}
\author{Gregory Haynes}

\begin{document}

\maketitle

\section*{Topic}
How can a machine vision system be developed which will provide functionality that rivals human vision?

\section*{Proposal}
\paragraph{}Artificial intelligence encompasses a wide variety of systems working in unison to develop a seemingly intelligent agent.  Each of these systems feature many of their own problems, many of which can be broken down into sub-systems.  One of these major systems is that of visual perception.

\paragraph{}The human visual perception system is truly a marvel.  Using only two light detection sources we are able to percieve all three dimensions seemingly on-the-fly.  While we see this as an extremely simple task, emulating this system takes vast ammounts of computational resources which we are only beginning to understand.  A new wealth of computational power has given hope for more advanced pattern recognition sytems which use digital imaging systems, while higher quality digital imaging in smaller devices has made implementing multiple digital video feeds in a mobile device feasible.

\paragraph{}Although visual perception systems have been researched for many years, new advances in technology change our abilities in this feel at an increasingly rapid pace.  This research project will shed light on some of these new systems which we may have before thought entirely infeasible and attempt to show where these new technologies are headed.

\end{document}
